---
title: "Overall summary report"
date: "`r Sys.Date()`"
output: pdf_document
fontsize: 12pt
params:
  dat: dat
  print_n_perc: print_n_perc
  summarise_num: summarise_num
  kable_table: kable_table
  time_format: time_format
  bp_file: bp_file
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
require("dplyr", quietly = TRUE)
```

## 1) Overall data summaries

Records | N (%)
-------------------------------------------------------|-------------
Number of rows read in | `r nrow(params$dat)`
Number of rows with valid BG value format | `r params$print_n_perc(n = sum(!is.na(params$dat$result)), total = nrow(params$dat))`
Number of rows with valid BG date/timestamp format | `r params$print_n_perc(n = sum(!is.na(params$dat$result_time)), total = nrow(params$dat))`
Number of rows with valid BG value and date/timestamp format | `r params$print_n_perc(n = sum(!is.na(params$dat$result_time) & !is.na(params$dat$result)), total = nrow(params$dat))`
Number of rows with valid BG value and date/timestamp format, and valid admission id and location* | `r params$print_n_perc(n = sum(!is.na(params$dat$result_time) & !is.na(params$dat$result) & !is.na(params$dat$admission_id) & !is.na(params$dat$location)), total = nrow(params$dat))`

*: Valid admission id and location means that the entry is not NA or blank 
(i.e., whitespace).

### Overall summary of BG variables

<!--
When reporting BG results: focus on rows with valid BG results.
When reporting BG timestamp: focus on rows with valid timestamps.
When reporting number of readings per admission-day: focus on rows with all 
four columns being valid.
-->

```{r, results='asis'}
if (params$time_format == "hm") {
  cat("Second was not included in the BG timestamp and was artificially inserted as 11 for completeness.\n")
}
if (params$time_format == "Not available") {
  cat("BG timestamp was not available in the input data and was artificially inserted as 11:11:11 AM for completeness.\n")
}
```

```{r, results='asis'}
count_adm_day <- params$dat %>% 
  filter(!is.na(admission_id), !is.na(date), !is.na(result), 
         !is.na(location)) %>% 
  group_by(admission_id, date) %>% 
  summarise(n = n())
# table2 <- rbind(params$summarise_num(params$dat$result), 
#                 params$summarise_num(params$dat$result_time), 
#                 params$summarise_num(count_adm_day$n, n_digits = 1))
table2_1 <- params$summarise_num(params$dat$result)
table2_2 <- format(params$summarise_num(params$dat$result_time), 
                   "%Y-%m-%d %H:%M:%S")
table2_3 <- params$summarise_num(count_adm_day$n, n_digits = 1)
table2 <- data.frame(row_names = c("Min", "1-th", "5-th", "25-th", "Mean", 
                                   "Median", "75-th", "95-th", "99-th", "Max"), 
                     result = table2_1, result_time = table2_2, 
                     count = table2_3, stringsAsFactors = FALSE)
params$kable_table(table = table2, 
                   colnames = c("[]()", "BG value", "BG date/timestamp", 
                                "Count of BG reading per admission-day"), 
                   width_row = "-------|----------|-------------------|--------------------------")
```

### Top 10 entries in BG variables

```{r, results='asis'}
# Top 10 are the largest
table3_1 <- sort(params$dat$result, decreasing = TRUE, na.last = TRUE)[1:10]
table3_2 <- format(sort(params$dat$result_time, 
                        decreasing = TRUE, na.last = TRUE)[1:10], 
                   "%Y-%m-%d %H:%M:%S")
table3_3 <- sort(count_adm_day$n, decreasing = TRUE, na.last = TRUE)[1:10]
table3 <- data.frame(row_name = 1:10, result = table3_1, result_time = table3_2, 
                     count = table3_3, stringsAsFactors = FALSE)
params$kable_table(
  table = table3, 
  colnames = c("[]()", "BG value", "BG date/timestamp", 
               "Count of BG reading per admission-day"), 
  width_row = "-------|----------|-------------------|--------------------------"
)
```

### Bottom 10 entries in BG variables

```{r, results='asis'}
table4_1 <- sort(params$dat$result, decreasing = FALSE, na.last = TRUE)[1:10]
table4_2 <- format(sort(params$dat$result_time, 
                        decreasing = FALSE, na.last = TRUE)[1:10], 
                   "%Y-%m-%d %H:%M:%S")
table4_3 <- sort(count_adm_day$n, decreasing = FALSE, na.last = TRUE)[1:10]
table4 <- data.frame(row_name = 1:10, result = table4_1, result_time = table4_2, 
                     count = table4_3, stringsAsFactors = FALSE)
params$kable_table(
  table = table4, 
  colnames = c("[]()", "BG value", "BG date/timestamp", 
               "Count of BG reading per admission-day"), 
  width_row = "-------|----------|-------------------|--------------------------"
)
```

<!-- pdflatex was not able to handle path to figure if we do not manually save 
boxplot to pdf. -->
```{r, include=FALSE}
pdf(file = params$bp_file, height = 4, width = 4)
boxplot(params$dat$result, main = "Boxplot of valid BG values")
dev.off()
vec_loc <- unique(params$dat$location[!is.na(params$dat$location)])
```

```{r, results='asis'}
cat("![](", params$bp_file, ")\n", sep = "")
```
<!-- Cannot remove the pdf after this line -->

Number of unique valid admission ids: 
`r length(unique(params$dat$admission_id))`.  
Number of admission-days: `r nrow(count_adm_day)`.  
Number of unique valid location: `r length(vec_loc)`.  
List the unique valid location: `r toString(sort(vec_loc))`.

## 2) Report of invalid readings

### Invalid BG values

```{r, results="asis"}
dat_inv_result <- params$dat[is.na(params$dat$result), ]
if (nrow(dat_inv_result) > 0) {
  table5 <- dat_inv_result %>% 
    group_by(result_raw) %>% 
    summarise(n_and_perc = params$print_n_perc(n = n(), 
                                               total = nrow(params$dat)))
  colnames(table5) <- c("Label", "N (%)")
  # If there are NA, annotate it
  row_na <- which(is.na(table5$Label))
  if (length(row_na) > 0) {
    table5$Label[row_na] <- "NA*"
  }
  params$kable_table(
    table = as.data.frame(table5), 
    colnames = c("Label", "N (%)"), 
    width_row = "-------|-------"
  )
  if (length(row_na) > 0) {
    cat("*: Blank and NA entries are reported as NA.\n")
  }
}
```

```{r, results="asis"}
if (nrow(dat_inv_result) == 0) {
  cat("There is no invalid BG values in the input data.\n")
}
```

### Invalid BG timestamps

```{r, results="asis"}
if (anyNA(params$dat$result_time)) {
  result_time_invalid <- sort(params$dat$result_time_raw[is.na(params$dat$result_time)])
  i_na <- which(is.na(result_time_invalid))
  if (length(i_na) > 0) {
    result_time_invalid[i_na] <- "NA*"
  }
  cat("The list of invalid BG timestamps are:\n", 
      toString(sort(result_time_invalid)))
  if (length(i_na) > 0) {
    cat("*: Blank and NA entries are reported as NA.\n")
  }
} else {
  cat("There is no invalid BG timestamp in the input data.\n")
}
```
